Fixed-Shape Ellipse by Three Points

### 2019-10-23 ONPCE/slides.tex
wip

The roots of $\xi$ are solutions of our problem.
	\begin{figure}
	\centering

@@

\begin{frame}{Fixed-shape ellipse by three points}
	There is no clear pattern in $\xi$.
	\begin{itemize}
		\item It can be written as 
		$$\xi(\theta)=\sum_{0 \le j, k \le Deg(\xi)} \alpha_{j,k}\cos^{j}{\theta}\sin^{k}{\theta}.$$
		\item Degree $6$, at most $12$ roots in $[0, 2\pi)$ \cite[p.~150]{powell}
	\end{itemize}
\begin{figure}
	\centering

	%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
	\includegraphics[scale=.4]{012}
	\caption{Another example of $\xi$.}
	%	\label{fig:circumscribed-circle}
\end{figure}
\end{frame}

@@

@@

\begin{frame}{Chebyshev Interpolation}{Roots}
	The roots of a Chebyshev polynomial can be found though determining the eigenvalues of a Chebyshev companion matrix \cite{boyd:2013}. For $n=5$ we have:

@@

	\begin{itemize}
		\item This matrix is a Hessenberg matrix.
		\item Its eigenvalues can be found by a QR decomposition in $\bigO(n^3)$.
	\end{itemize}
\end{frame}

>>>>

	\begin{itemize}
		\item It can be written as 
		$$\xi(\theta)=\sum_{0 \le j, k \le Deg(\xi)} \alpha_{j,k}\cos^{j}{\theta}\sin^{k}{\theta}.$$
		\item Degree $6$, at most $12$ roots in $[0, 2\pi)$ \cite[p.~150]{powell}
		\item The roots of $\xi$ are solutions of our problem.	
\end{itemize}

\begin{frame}{Fixed-shape ellipse by three points}
	An example with no roots.
	\begin{figure}
		\centering

@@

@@

	%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
	\includegraphics[scale=.5]{012}
	\caption{Another example of $\xi$.}
	%	\label{fig:circumscribed-circle}
\end{figure}
\end{frame}

\begin{frame}{Fixed-shape ellipse by three points}
	An example with four roots.
	\begin{figure}
		\centering

@@

\begin{frame}{Chebyshev Interpolation}{Roots}
	The roots of a Chebyshev polynomial can be found though determining the eigenvalues of a Chebyshev companion matrix \cite{boyd:2013}. For $n=5$, we have:

@@

	\begin{itemize}
		\item This is a Hessenberg matrix.
		\item Its eigenvalues can be found by a QR decomposition in $\bigO(n^3)$.
	\end{itemize}
\end{frame}
